% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
%

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,10pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\robustify\cftdotfill

%-----------------------------------------------------------
%Edit these values as you see fit
\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------
%Margin setup
\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{-0.25in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.75in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}

\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------
\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

\textbf{{\Large Ernita Dewi Puspitasari}} & Jakarta, Indonesia \\
\texttt{ernita.dewi91@gmail.com} & \textbf{\today} \\
\texttt{+6281380260279}

\end{tabular*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Summary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Finance professional in fast moving consumer goods industry with solid experience as auditor in \textit{Big-4} accounting firms. Skilled in planned and prepared financial statements in accordance with financial accounting standards and international audit standards, as well as in dealing with Indonesia's taxation regulation. With a \textit{can do} attitude, I always accept new challenge, adapt quickly, and strive to give real impact to the organization.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Work Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

  \item
  \ressubheading{Reckitt Benckiser}{Jakarta, Indonesia}{General Accounting and Account Payable Manager}{October 2021 - present}
  \begin{itemize}
    \resitem{Handle day-to-day operations in account payable and treasury transactions.}
    \resitem{Generate monthly report and prepare for fluctuation analysis for the balance sheet account.}
    \resitem{Review month-end-closing journal entries.}
    \resitem{Review balance sheet reconciliation in monthly basis}
    \resitem{Consolidate forecasted cash flow in foreign currency for external hedging plan.}
    \resitem{Maintain relationship with bank partners to optimize cash management.}
    \resitem{Liaise with internal control to ensure the control has been implemented and allign with global policy.}
    \resitem{Liaise with external auditors for the audited financial statement.}
    \resitem{Lead adhoc projects to transform the existing worklog to increase its efficiency.}
    \resitem{Report directly to Finance Controller.}
    \resitem{Manage 15 team members of account payable, travel and expenses, treasury, intercompany, and general accounting.}
  \end{itemize}

  \item 
  \ressubheading{Payfazz Financial Group}{Jakarta, Indonesia}{Finance and Accounting Manager}{November 2019 - October 2021(2 years)}
  \begin{itemize}
    \resitem{Handled end-to-end financial process in Fazz Financial Group.}
    \resitem{Evaluated efficiency and effectiveness of accounting processes, and proposed recommendations to optimize them.}
    \resitem{Prepared and analyzed financial statement in monthly basis.}
    \resitem{Designed and implemented automated journal entry for new product by collaborating with product team as well as financial engineer.}
    \resitem{Analyzed the impact of foreign operations on reported financial results, including foreign exchange transactions.}
    \resitem{Ensured integrity, accuracy, and completeness of financial statements by discussing the need for and nature of appropriate disclosures.}
    \resitem{Reported directly to VP Finance and Accounting.}
    \resitem{Managed 5 team members in finance and accounting.} 
  \end{itemize}

\item 
\ressubheading{PricewaterhouseCoopers}{Jakarta, Indonesia}{Senior Associate Auditor}{August 2019 - November 2019 (3 months)}
\begin{itemize}
  \resitem{Similar responsibility with my previous role in PwC but with a bigger client allocation.}
\end{itemize}

\item
\ressubheading{Freelance}{Stockholm, Sweden}{Accountant}{July 2018 - September 2018 (3 months)}
\begin{itemize}
  \resitem{Prepared statements of financial position and income statement of profit and loss for the client.}
\end{itemize}

\item
	\ressubheading{PricewaterhouseCoopers}{Jakarta, Indonesia}{Senior Associate Auditor}{June 2013 - January 2017 (3 years 7 months)}
  \begin{itemize}
    \resitem{Planned audit procedures that allign with auditing standard and PSAK as well as prepared the budgets and resources to ensure the audit would go smoothly.}
    \resitem{Coordinated the team and its audit assignments to ensure that the team was aware of clients' business processes and current relevant issues that might impact their audit procedures.}
    \resitem{Identified and assessed risk of material misstatements of financial statements due to fraud, and assessed internal control (if necessary) to ensure the control is effective.}
    \resitem{Designed and implemented responses to material misstatement including performed and tested the appropriateness of  journal entry testing.}
    \resitem{Communicated audits findings to the manager and the clients effectively.}
	\end{itemize}

\item
	\ressubheading{Deloitte}{Jakarta, Indonesia}{Junior Auditor}{January 2013 - May 2013 (5 months)}
  \begin{itemize}
    \resitem{Responsible in doing financial audits in a particular area such as cash and cash equivalent, account payable, advance and pre-payment, property plant and equipment, and general and administrative expenses.}
	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
	\ressubheading{Universitas Indonesia}{Jakarta, Indonesia}{Bachelor of Economics, Accounting}{Agustus 2009 - February 2013}
	\begin{itemize}
    \resitem{Graduated Magna Cum Laude with a Bachelor of Economics degree in 3.5 years.}
    \resitem{Assisted a number of lectures including principal accounting, quantitative method in business, and investment management.}
    \resitem{Extracurricular: Financial controller in the Student Executive Board (BEM UI) with the responsibility to manage and keep track of monthly budget for all departments as well as to report financial statements of the organization.}
	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Skills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
  \item Financial audit and accounting.
  \item Analyzing income and deferred tax calculation.
  \item Working with numbers and analyzing statistical and financial data.
  \item Analyzing financial statements and draft reports.
  \item Expert in Microsoft Excel and fast learner in using any financial software on demand.
  \item Managing a team in terms of resources allocation, budgeting, and time management.
  \item Excellent in using SAP System.
\end{itemize}

\resheading{External Courses}
\begin{itemize}
  \item PSAK for Professional (IAI - 2021)
\end{itemize}

\end{document}